### 2012-02-06 docs/architecture/architecture.tex
reference evolving boxlib manual
update to describe new directoy layout

  Simple Fortran-based analysis routines (e.g.\ extract a line from a
  multidimensional dataset) that operate on BoxLib datasets.

@@

  External modules, like ODE integrators, equations of state, reaction
  networks

@@

    An integration package for ODEs.  At the moment, this is used for
    integrating various reaction networks.

@@

  The main \maestro\ algorithm directory.  The individual problem
  directories lie under here, and all of the main \maestro\ source
  lives in the {\tt Source/} sub-directory.

@@

@@

  \item problem directories: {\tt test2}, {\tt test\_spherical},
    $\ldots$

    Each problem in \maestro\ gets it own sub-directory.  The {\tt
      GNUmakefile} in the problem directory includes the instructions
    on how to build the executable, including what modules in {\tt
      extern} are used.

    Any file that you place in a sub-directory here takes precedence
    over a file of the same name in {\tt MAESTRO/}.  This allows
    problems to have custom versions of the main \maestro\ routines
    (e.g.\ initial conditions via {\tt initdata.f90}.  See
    \S~\ref{sec:makefile} for details on the build system).

@@

To simplify the description of the underlying AMR grid, BoxLib
provides a number of Fortran types.  We briefly summarize the major
data types below.

>>>>

  Simple Fortran-based analysis routines (e.g.\ extract a line from a
  multidimensional dataset) that operate on BoxLib datasets.  These are
  described in \S~\ref{sec:analysis}.

  Several sub-directories with python-based routines are also here.
  These are described both in \S~\ref{sec:analysis} and \S~\ref{sec:vis:python}.

@@

  External modules, like ODE integrators, equations of state, reaction
  networks, etc.  Many of these routines were developed by other groups.

@@

    The {\tt VODE} \cite{vode} package for integrating ODEs.  At the
    moment, this is used for integrating various reaction networks.

@@

  The main \maestro\ algorithm directory.

  Each problem in \maestro\ gets it own sub-directory under {\tt
    SCIENCE/}, {\tt TEST\_PROBLEMS/}, or {\tt UNIT\_TESTS/}.  The {\tt
    GNUmakefile} in the problem directory includes the instructions on
  how to build the executable, including what modules in {\tt extern}
  are used.  Any file that you place in a sub-directory here takes
  precedence over a file of the same name in {\tt MAESTRO/}.  This
  allows problems to have custom versions of the main
  \maestro\ routines (e.g.\ initial conditions via {\tt initdata.f90}.
  See \S~\ref{sec:makefile} for details on the build system).

@@

  \item {\tt SCIENCE/}

    \maestro\ problem directories for science studies.  These are the
    setups that have been used for science papers in the past, or are
    the basis for current science studies.

@@

  \item {\tt TEST\_PROBLEMS}

    \maestro\ problem directories for simple test problems that have
    been used while developing \maestro.  Many of these problems have
    appeared in the various papers describing the \maestro\ algorithm.

  \item {\tt UNIT\_TESTS}

    Special \maestro\ problem directories that test only a single component
    of the \maestro\ algorithm.  These often have their own main drivers
    ({\tt varden.f90}) that setup and initialize some data structures and
    then call only a few of the \maestro\ routines.  See \S~\ref{sec:unit_tests}
    for details.

@@

To simplify the description of the underlying AMR grid, BoxLib
provides a number of Fortran types.  We briefly summarize the major
data types below.  A more extensive introduction to \boxlib\ is 
provided by the \boxlib\ User's Guide, distributed with the library.
